\newcommand\version{v1}
\problemname{Mafia 2}
A mafia has infiltrated the city \texttt{<insert name here>}.
This has made the police force of \texttt{<insert name here>} very confused, with accusations of corruption being made in every direction.
The city's $N$ cops (which are numbered between $0$ and $N - 1$) has made a number of accusations about other policemen.
Each accusation is either:
\begin{enumerate}
  \item Police number $i$ is an honest cop.
  \item Police number $i$ is a corrupt cop.
\end{enumerate}.
An honest cop always tells the truth, while a corrupt cop always lies.
In total, there has been $M$ accusations.

From last time, the chief of police knows how to interpret these accusations: if police $x$ accuse police $y$ of being honest,
this means that either both of them are honest or none of them are. In the same way, if $x$ accuse police $y$ of being corrupt,
then exactly one of them must be honest and exactly one of them must be corrupt.

However, it seems that she must have recorded some of the accusations incorrectly. It turns out that the accusations of the 
policemen are inconsistent with the model of honest and corrupt cops -- there is no partition of the cops into honest
and corrupt cops such that all the accusations are true.

Determine a set of accusations that \emph{is} consistent -- i.e. there exists a partition of cops into honest and corrupt cops
such that all accusations are true -- with as large size as possible.

\section*{Example}
Let there be $N = 3$ cops, and $M = 3$ accusations.

Each cop accuses another of being corrupt in a triangle, so that first accuse the second, the second accuse the third, and the third
accuse the first.

Since accusing another policeman of being corrupt is equivalent to exactly one of them being corrupt, these three accusations
are inconsistent. If we let the first police be honest, the second must be corrupt, so the third one is honest, but not both
the first and third police can be honest.

A largest set of accusations that is consistent can be obtained by chosing any two accusations. Say that we keep the accusations
of the first and second policemen. Then it is possible that the first and third policemen are indeed honest, and the second
is corrupt.

\section*{Task}
This task is output-only. You will be able to download the input from the judging system, and should submit only your output files
to the judge.

\section*{Subtasks}
The problem will consist of 10 input files. Each file will give between 0 and 10 points.

For a certain test case $i$, let
\begin{itemize}
  \item $C_i$ be the size of the largest set found by a contestant
  \item $X_i$ be the size of the set you found
\end{itemize}
Let the size of the best set found for a certain test case $i$ be $B_i$, and the size of your set is $X_i$. Then, your score will be
\[ 10 \cdot \max\{ 0, \frac{X_i - 0.5}{C_i - 0.5} \} \]

\end{tabular}

\section*{Input format}
\begin{itemize}
  \item line $1$: \texttt{N M}: the number of policemen and the number of accusations, respectively.
  \item line $2$: \texttt{A[0] ... A[M - 1]}: for each $i$, $A[i]$ contains the number of the police who made the $i$:th accusation.
  \item line $3$: \texttt{B[0] ... B[M - 1]}: for each $i$, $B[i]$ contains the number of the police was the target of the $i$:th accusation.
  \item line $4$: \texttt{T[0] ... T[M - 1]}: for each $i$, $T[i]$ contains 1 if the $i$:th accusation was of a policeman's honesty, and 0 if it was of a policeman's corruptness.
\end{itemize}

\section*{Output format}
Your output should consist of $M$ integers. The $i$:th integer should be 0 (if the $i$:th accusation is not part of your selected set) or 1 (if the $i$:th accusation is part of your selected set).
