\newcommand\version{v1}
\problemname{Surveillance}
A crime has been committed in the city of \texttt{<insert name here>}! \emph{All} of the donuts in the bakery next to the police station
has mysteriously disappeared. Since this is the favourite bakery of the police, every resource available will be used to find the thief.

The police has made a list of suspected donut thieves, but there is no evidence against anyone yet.
Luckily, there is security footage from the scene of the crime. Unfortunately it takes way too long time
to watch all of the footage to be done before the expiry date of the donuts has passed.

Therefore, you have been tasked with writing a program to find the cookie thieves in the images.
Your program will be given a $W \times W$ image of a suspected cookie thief, and a $B \times B$
image from the security footage. An image consists of a rectangular array of pixels, which we
represent as integers.

Your program should count the number of occurances of the cookie thief image inside the security footage image.
We say that a $W \times W$ subrectangle of the security footage contains the cookie thief image if there exists
some constant $C$ such that every pixel in the subrectangle equals the corresponding pixel in the cookie thief image
plus $C$. This is because the images may have been taken using different exposure settings, meaning one of the images
can be lighter than the other.


\section*{Example}
Let the security footage be
\[
\begin{bmatrix}
  1 & 2 & 3 & 4 \\
  1 & 2 & 3 & 4 \\
  4 & 3 & 3 & 4 \\
  4 & 3 & 3 & 4
\end{bmatrix}
\]
and the cookie thief image is
\[
\begin{bmatrix}
  0 & 1 \\
  0 & 1
\end{bmatrix}
\]

Then there are five matches in the security footage: those areas with upper left corners in $(0, 0), (0, 1), (0, 2), (1, 2), (2, 2)$ (denoted by $(row, column)$).
The constants $C$ are $1, 2, 3, 3, 3$ respectively.

\section*{Task}

TODO

\begin{itemize}
  \item \texttt{surveillance(B, W, S, T)} - this function will be called exactly once by the judge.
  \begin{itemize}
    \item \texttt{B}: an integer - the size of the security footage image.
    \item \texttt{W}: an integer - the size of the cookie thief image.
    \item $W \le B$
    \item \texttt{S}: a two-dimensional array with $B \times B$ integers. \texttt{S[i][j]} ($0 \le i, j < B$) contains the value of the pixel on row $i$ and column $j$ in the security footage image.
    \item \texttt{T}: a two-dimensional array with $W \times W$ integers. \texttt{T[i][j]} ($0 \le i, j < W$) contains the value of the pixel on row $i$ and column $j$ in the cookie thief.
    \item $0 \le S[i][j], T[i][j] \le 10^9$
    \item The function should return an integer, the number of matches in the image.
  \end{itemize}
\end{itemize}

\section*{Subtasks}
The problem consists of a number of subtasks. Each subtask gives some amount of points, and to pass
the subtask you must pass all the test cases in the subtask.

\begin{tabular}{|l|l|l|}
  \hline
  \textbf{Subtask} & \textbf{Points} & \textbf{Limits} \\ \hline
  1 & 7 & $1 \le W = B \le 1\,000$  \\ \hline

  2 & 14 & $1 \le B \le 1\,000$, $0 \le T[i][j], S[i][j] \le 1$ \\ \hline

  3 & 24 & $1 \le B \le 1\,000$, $0 \le T[i][j], S[i][j] \le 128$ \\ \hline

  4 & 55 & $1 \le B \le 1\,000$ \\ \hline

\end{tabular}

\section*{Input format}
The sample judge reads input in the following format:

\begin{itemize}
  \item line $1$: \texttt{B W}
  \item line $i = 2$ to $2 + B - 1$: \texttt{B[i][0] B[i][1] ... B[i][B - 1]}
  \item line $i = 2 + B$ to $2 + B + W - 1$: \texttt{W[i][0] W[i][1] ... W[i][B - 1]}
\end{itemize}

\section*{Output format}
The judge writes a single line containing the return value of \texttt{surveillance(B, W, S, T)}.
