\problemname{Free food}

Hsara loves free food.

Tonight Hsara is going out for a dinner at a restaurant with her organisation and Hsara is thinking about the chances of someone else paying for the dinner. Exactly one person will pay for the entire dinner (everyone's food), but not any person. It is only allowed to pay for dinner if no supperior (possibly indirect, for example, your boss' boss) in the organisation is present at the table.

The organisation consists of $N$ people numbered from $1$ to $N$. Each person, except for the CEO, has exactly one boss. Given each person's boss and a list of people present at the table, determine how many people are able to pay for the dinner.

\section*{Input}

The first line consists of two integers, $N$ - the number of people in the organisation and $M$ - the 

Den första raden i indatan innehåller två heltal, $N$ - antalet personer i organisationen och $M$ - antalet personer vid bordet.

Den andra raden innehåller $N$ heltal. Det $i$:te talet anger vem som är chef till person $i$. 0 innebär att personen inte har en chef och därmed är VD för organisationen. Det finns precis en person som är VD.

Den tredje raden innehåller $1 \le M \le N$ heltal som anger vilka som sitter vid bordet.

\section*{Output}
Skriv ut ett heltal - antalet personer vid bordet som skulle kunna betala för middagen.

\section*{Poängsättning}
Din lösning kommer att testas på en mängd testfallsgrupper. För att få poäng för en grupp så måste du klara alla testfall i gruppen.

\begin{tabular}{| l | l | l |}
	\hline
	Grupp & Poängvärde & Begränsningar\\ \hline
  1     & 49         & $2 \le N \le 2\,000$ \\ \hline
  2     & 51         & $2 \le N \le 100\,000$. \\ \hline
\end{tabular}

\section*{Förklaring}
I det första exemplet kan personerna 1 och 2 betala. Person 3 kan inte betala eftersom person 1 sitter vid bordet.

I det andra exemplet är person 5 VD och sitter vid bordet. Därför kan bara person 5 betala.
