\problemname{Tic-Tac-Toe}
M책rten is extremely good at tic-tac-toe.
He's so good you've never managed to beat him.
Write a program that plays tic-tac-toe for you, and you might have a chance.

If you don't know the rules of the game, you can read them \href{https://en.wikipedia.org/wiki/Tic\_tac\_toe}{on Wikipedia}.

\section*{Interactivity}
This problem is interactive.
First, you should read one line containing either \texttt{first} or \texttt{second}, depending on whether you move first or not.

Then, you should repeatedly read in a tic-tac-toe grid containing the current game state (blank if you're making the first move, otherwise containing M책rten's last move).
After reading the grid, you should output a grid with the move you performed.

If you output a grid where you win or play a draw your program should terminate.
If you read a grid where M책rten won or drew your program should terminate.

A grid is output and read as a 3 lines with 3 characters each -- \texttt{.} for an empty square, \texttt{o} for M책rten's pieces, or \texttt{x} for your pieces (note lower-case letters).

\section*{Grading}
Your solution will be tested on several groups of test cases. To get points for a group you need to pass all the tests of that group.

\noindent
\begin{tabular}{| l | l | l |}
	\hline
	Group & Points & Constraints\\ \hline
 $1$    & $20$        & You must play a valid game. \\ \hline
 $2$    & $25$        & You must never lose a game. \\ \hline
 $3$    & $30$        & You must always win a game if possible. \\ \hline
 $4$    & $25$        & You must never lose a game and you must always win a game of possible. \\ \hline
\end{tabular}
